Parameter Estimation for the CES Model

### 2013-07-24 CES.Rnw
Trying to get xtable to work.

# Make all the models
kleModels <- ldply(countryAbbrevs, fitCES, nest="(kl)e")
lekModels <- ldply(countryAbbrevs, fitCES, nest="(le)k")
eklModels <- ldply(countryAbbrevs, fitCES, nest="(ek)l")
allModels <- rbind(kleModels, lekModels, eklModels)
#modelMatrix <- cbind(kleModels, lekModels, eklModels)
#colnames(modelTable) <- nestingOptions

@@

>>>>

# Make all the models
kleModels <- ldply(countryAbbrevs, fitCES, nest="(kl)e")
lekModels <- ldply(countryAbbrevs, fitCES, nest="(le)k")
eklModels <- ldply(countryAbbrevs, fitCES, nest="(ek)l")
allModels <- rbind(kleModels, lekModels, eklModels)

CESTable <- xtable(allModels, caption="CES coefficients.", label="tab:CES-coeffs-table")

#modelMatrix <- cbind(kleModels, lekModels, eklModels)
#colnames(modelTable) <- nestingOptions

@@

<<Print_CES_Tables, results='asis'>>=
CESTable
@
